\textbf{Providing Access Control and Copy-on-Write for Content Distribution Network Assets}

### 2016-04-13 tex/paper.tex
Changed some effect to affect

The research question that this report tries to answer is how and whether it is practically 
feasible to use Copy-on-Write for a high-level system like the one that is implemented and how 
it can effect the system's scalability.

@@

\end{description}
\newpage
\section{Model} \label{sec:model}
This section describes how different operations can be expected to effect the data in the system.
The model for this work also shows how the data can only be accessed or modified by
authorized users and how the defined integrity of the data is always kept.

@@

\subsection{Data integrity}
A computer system or subsystem is defined as possessing the property of integrity if it behaves consistently
according to a defined standard. This implies that a subsystem possessing the property of integrity
does not guarantee an absolute behaviour of the system, but rather that it performs according to
what its creator intended ~\cite{BIBA}.
\\
The invariant for this model is the file. Which means that it should not be possible to
change a file though out the cycle of operation without creating a new file object with a new
identifier. This is to ensure that files can not lose their integrity by simultaneous
operations from different nodes or get mixed up when referred to from a content object.

\subsection{Initial Assumptions}
To create an integrity model, some initial assumptions have to be made about what the correct
behaviour of the system is, which the model then can be shown to follow. In this work unintentional
behaviour as the result of data modification is the main concern, which could be used for sabotage
or simply be the effect unintentional unfortunate race conditions etc.

@@

To describe a content object \textit{m} containing fileId \textit{f}, the following syntax is used:
$[fileId = f.id, \dots] \in M$, the same syntax is also applied to different types of objects
throughout the explanation of the model.

@@

These predicates are used in several places and are therefore named \textit{*}.

@@

\subsection{Copy-on-Write's effect on Scalability}
As no comparison with solutions that were not Copy-on-Write based were made, no scientific
conclusions can be drawn from how its effect was on the scalability of the system. However some
intuitively drawn conclusions can be suggested. If comparing to a system which uses a SQL database
the Copy-on-write system would have an easier time to scale on the width as no global locks or
transactions has to be used, which with high probability would slow down the system, especially when
widely distributed.
The gain of having the locks or transactions would be that the system would
always be in a fully consistent state. The loss would be that all of the database nodes would need
to constantly have to, in some sense, be fully aware of the state of the other nodes.
Sharding~\cite{SHARDING} could be used to minimise the communication of state between the nodes, but
that results in less fault tolerance and possibly higher loads on some nodes than others due to that
the data most likely will not be accessed uniformly.

>>>>

The research question that this report tries to answer is how and whether it is practically 
feasible to use Copy-on-Write for a high-level system like the one that is implemented and how 
it can affect the system's scalability.

@@

\end{description}
\newpage
\section{Model} \label{sec:model}
This section describes how different operations can be expected to affect the data in the system.
The model for this work also shows how the data can only be accessed or modified by
authorized users and how the defined integrity of the data is always kept.

@@

\subsection{Data integrity}
A computer system or subsystem is defined as possessing the property of integrity if it behaves consistently
according to a defined standard. This implies that a subsystem possessing the property of integrity
does not guarantee an absolute behaviour of the system, but rather that it performs according to
what its creator intended ~\cite{BIBA}.
\\
The invariant for this model is the file. Which means that it should not be possible to
change a file though out the cycle of operation without creating a new file object with a new
identifier. This is to ensure that files can not lose their integrity by concurrent
operations from different nodes or get mixed up when referred to from a content object.

\subsection{Initial Assumptions}
To create an integrity model, some initial assumptions have to be made about what the correct
behaviour of the system is, which the model then can be shown to follow. In this work unintentional
behaviour as the result of data modification is the main concern, which could be used for sabotage
or simply be the effect of unintentional race conditions etc.

@@

To describe a content object \textit{m} containing fileId \textit{f}, the following syntax is used:
$\{id = \dots , file = f\} \in M$, the same syntax is also applied to different types of objects
throughout the explanation of the model. The \"fresh\" keyword applied to id means that it is a new
globally unique identifier.

@@

The predicates in (\ref{eq:fileread}) are used in several places and are therefore named \textit{*}.

@@

\subsection{Copy-on-Write's effect on Scalability}
As no comparison with solutions that were not Copy-on-Write based were made, no scientific
conclusions can be drawn from what its effect was on the scalability of the system. However some
intuitively drawn conclusions can be suggested. If comparing to a system which uses a SQL database
the Copy-on-write system would have an easier time to scale on the width as no global locks or
transactions has to be used, which with high probability would slow down the system, especially when
widely distributed.
The gain of having the locks or transactions would be that the system would
always be in a fully consistent state. The loss would be that all of the database nodes would need
to constantly have to, in some sense, be fully aware of the state of the other nodes.
Sharding~\cite{SHARDING} could be used to minimise the communication of state between the nodes, but
that results in less fault tolerance and possibly higher loads on some nodes than others due to that
the data most likely will not be accessed uniformly.
